---
title: "Survey"
author: "Scott Brenstuhl"
date: "February 23, 2016"
output: html_document
---

```{r echo = FALSE}
library(dplyr)
library(readr)
library(ggplot2)
library(reshape2)
library(plotly)
```



```{r, echo=FALSE}
# Originally from SF Open Data
# https://data.sfgov.org/City-Management-and-Ethics/San-Francisco-City-Survey-Data-1996-2015/89tc-4uwi

# setwd('/Users/scottbrenstuhl/Projects/Data_Science_Projects/SF_city_survey')

city.survey <- read_csv('data/San_Francisco_City_Survey_Data_1996-2015.csv')
#unique(city.survey$finweigh)

```

Ideas:
    Things by zipcode over time
    Parents vs not
    % of respondents with kids over the years (maybe also by zip)
    Peoples own neighborhoods vs city wide (by zip too)
    Correlation between cleanliness, lights, etc. and safety
    Match up Zipcode info with census data see how incomes etc. play in
    Tell the story of the mission & SOMA since people talk about them changing so much
        Mission zipcode: 94110
        SOMA: 94103
    Do changes over the years match up with 311 call learnings?
    All kinds of demographics info. 
        Does it line up with Census data?
        People per household, up or down?
        Own or rent home
    What do people say in open ended comments? 
        
Questions:
    How do I do the weighting for finweigh
    Neighborhoods mapped to zips?
    
    
regression table
Arima, forcast package

6 and 7 should probably be made NA
```{r, echo=FALSE}
sidewalks <- group_by(city.survey, swclnbrd, swclcity) %>% 
            summarise(count = n())

ggplot(sidewalks, aes(swclnbrd, swclcity)) +
    geom_point(aes(size=count)) +
    labs(title = 'Cleanliness of Sidewalks',
         x = 'Own Neghborhood', y = 'The City')

sidewalks.sub <- subset(city.survey, zipcode %in% c(94110, 94103)) %>%
    group_by(swclnbrd, swclcity) %>%
    summarise(count = n())

# lol this seems useless
ggplot(sidewalks.sub, aes(swclnbrd, swclcity)) +
    geom_point(aes(size=count)) +
    labs(title = 'Cleanliness of Sidewalks (Mission &SOMA residents)',
         x = 'Own Neghborhood', y = 'The City')

```

This needs to be a lot more digestable to be useful
2015, zip = NA remove after finding out why
```{r, echo=FALSE}
sidewalks_year <- group_by(city.survey, year, zipcode) %>% 
            summarise(mean_rating = mean(swclnbrd, na.rm= TRUE), count = n())
sidewalks_year <- subset(sidewalks_year, year > 2003)

ggplot(sidewalks_year, aes(year, mean_rating, color = zipcode))+
    geom_point() +
    geom_line() +
    labs( title = 'Sidewalk cleanliness over time by neighborhood',
          x= 'Year', y = 'Mean Rating of Own Neighborhood')

sidewalks_year <- subset(sidewalks_year, year > 2003 & zipcode %in% c(94110, 94103))

ggplot(sidewalks_year, aes(year, mean_rating, color = zipcode))+
    geom_point() +
    geom_line() +
    labs( title = 'Sidewalk cleanliness over time by neighborhood',
          x= 'Year', y = 'Mean Rating of Own Neighborhood')


```


Lolllllllll Need a lot of zip cleaning and a better plan than facets
```{r, echo=FALSE}
# sidewalks_zips <- group_by(city.survey, swclnbrd, swclcity, zipcode) %>% 
#             summarise(count = n())
# 
# ggplot(sidewalks, aes(swclnbrd, swclcity)) +
#     facet_grid(zipcode ~ .) +
#     geom_point(aes(size=count)) +
#     labs(title = 'Cleanliness of Sidewalks',
#          x = 'Own Neghborhood', y = 'The City')

```


```{r, echo=FALSE}
parents.by.year <- group_by(city.survey, year, kids) %>%
    summarise(count = n()) %>%
    group_by(year) %>%
    mutate(year_count = sum(count)) %>%
    group_by(kids) %>%
    mutate(percent = (count/year_count)*100)

plot.parents <- subset(parents.by.year, kids == 1)
ggplot(plot.parents, aes(year, percent)) +
    geom_point() +
    geom_line() +
    labs(title = "% of respondents with children")

```

```{r, echo=FALSE}
parents.by.year.zip <- group_by(city.survey, year, kids, zipcode) %>%
    summarise(count = n()) %>%
    group_by(year, zipcode) %>%
    mutate(year_count = sum(count))%>%
    group_by(kids) %>%
    mutate(percent = (count/year_count)*100)

#plot.parents.zip <- subset(parents.by.year.zip, kids == 1 & zipcode %in% c(94110, 94103))
plot.parents.zip <- subset(parents.by.year.zip, kids == 1)
p <- ggplot(plot.parents.zip, aes(year, percent, color=zipcode)) +
    geom_point() +
    geom_line() +
    labs(title = "% of respondents with children by zip")

ggplotly(p)

plot.parents.zip <- subset(parents.by.year.zip, kids == 1 & zipcode %in% c(94110, 94103))
#plot.parents.zip <- subset(parents.by.year.zip, kids == 1)
p <- ggplot(plot.parents.zip, aes(year, percent, color=zipcode)) +
    geom_point() +
    geom_line() +
    labs(title = "% of respondents with children by zip")

ggplotly(p)   
```

The groupings in this changes so need to account for that.
```{r echo = FALSE}
#how long in sf
length.of.residence <- group_by(city.survey, dlivedsf, year) %>%
    summarize(count = n()) %>%
    group_by(year) %>%
    mutate(year_count = sum(count)) %>%
    group_by(dlivedsf) %>%
    mutate(percent = (count/year_count)*100, dlivedsf2= as.character(dlivedsf))
# make dlivedsf a factor of charicter 

ggplot(length.of.residence, aes(year, percent, color=dlivedsf2)) +
    geom_point() +
    geom_line() +
    labs(title = '% of people lived in SF for x years')
```

```{r echo=FALSE}
#How likely to move from sf in next 3 years
leaving <- group_by(city.survey, movesf, year) %>%
    summarize(count = n()) %>%
    group_by(year) %>%
    mutate(year_count = sum(count)) %>%
    group_by(movesf) %>%
    mutate(percent = (count/year_count)*100, movesf2 = as.character(movesf))%>%
    subset(year >= 2005)

ggplot(leaving, aes(year,percent, color = movesf2)) +
    geom_point() +
    geom_line()+
    labs(title = 'Likelyhood to move out of SF')
    

```

